Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
fix typo in conclusion

Within a supervised setting of acoustic scene classification (ASC), we have shown the comparative benefits of log-scattering features over MFCCs, of majority voting at a mid-level time scale of $T=372\,\mathrm{ms}$ over prediction at a high-level time scale of $T=24\,\mathrm{ms}$, and of an adapted Gaussian kernel over the linear kernel in support vector machine (SVM) classification.
%, identified in the time domain in the unsupervised setting and in the features domain in the supervised case, provided that the dimensionality is sufficiently high. \ja{I'm not sure what this last part means.}

>>>>

Within a supervised setting of acoustic scene classification (ASC), we have shown the comparative benefits of log-scattering features over MFCCs, of majority voting at a mid-level time scale of $T=372\,\mathrm{ms}$ over prediction at a high-level time scale of $T=24\,\mathrm{s}$, and of an adapted Gaussian kernel over the linear kernel in support vector machine (SVM) classification.
%, identified in the time domain in the unsupervised setting and in the features domain in the supervised case, provided that the dimensionality is sufficiently high. \ja{I'm not sure what this last part means.}
